\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}

\begin{document}

\noindent Dear SW23 Special Issue Editors,
\\



We submit minor revisions to our article \textbf{Towards Sharing Tools and Artefacts for Reusable Simulations in Healthcare} (ARTICLE: 238598209). 

\textit{\textbf{Please note, as our work is based around open science, we would like to waive the double blind peer review process.}}

We have made amendments to the manuscript (changes are highlighted in red) and have provided a detailed point by point response to the two reviewers.  We would first like to draw the editor's attention to the following two key changes that were flagged up as the most important by the Editor in Chief:

\begin{enumerate}
    \item To address reviewer 1's concern about the technical content and readability, we followed their recommendation and restructured. We  have split section 4 into two and provided more introductory text to the technical content.  We now have a general overview section (4) + a technical section (5)(with an improved introduction, and increased signposting to figure 2). 
    \item We have followed reviewer 1's recommendation to make better use of tables to aid readability and and expanded Table 3. This now contains an easy to follow list of artefacts related to the manuscript and where to find them.
 \item We have addressed reviewer 2's concerns about the manuscript being too focused on the UK NHS.  We have updated figure 1 and removed the NHS logo and updated the discussion section to refer to healthcare more generally.

\end{enumerate}

We have made the following additional changes which also improves the readability of the manuscript:

\begin{itemize}
    \item As reviewer 1 recommended, we have re-emphasised the importance of documentation to enable model reuse.
    \item We have reworked part of the aims and discussion sections to address reviewers 2's concerns about a lack of clarify if research objectives had been achieved.
    \item We have made several rephrasing of sentences as suggested by reviewer 2.

\end{itemize}

We would also like to draw the editor's attention to reviewer 2's request for additional tables and charts of the literature review section.  We have responded to the reviewer and explained that the outputs they are requested are contained within our earlier JoS publication [1] that we cite in the main text. Our reasoning for not including here is that we conducted and published [1] in order to evidence the gap in the DES literature and allow us to do novel research to address it. This section is meant as a summary of the gap and is not part of the main contribution of the manuscript. We hope you agree.

\textbf{We note that the word count is now 10,300 words}.  Given the lack of open science knowledge in modelling and simulation we included substantial background section describing literature and state-of-the-art. Readers will best placed to understand and adopt our methods if they are more familiar with this area.

\vspace{0.2cm}


\noindent Yours faithfully,

\vspace{0.2cm}
\noindent Dr Thomas Monks (on behalf of the study team)

\section*{References}

[1] Thomas Monks \& Alison Harper (2023) Computer model and code sharing practices in healthcare discrete-event simulation: a systematic scoping review, Journal of Simulation, DOI: 10.1080/17477778.2023.2260772 

\end{document}
